\sysfull

### 2017-08-07 paper/systemdescription.tex
Compiler section revised (yaay)

\textbf{\sys Programming Model:} To use \sys, a programmer first writes plain, imperative C code. The programmer then has an option to {\em manually} or {\em automatically} translate the program into code for \sys's task-based programming model. To manually translate, the programmer decomposes the program into tasks, and annotates memory accesses that manipulate data shared by multiple tasks. To automatically translate, the programmer simply uses \sys's compiler (described in Section~\ref{sec:compiler}), which decomposes a program into tasks and annotates accesses to task-shared data. After translating to task-based code and compiling, the programmer has an executable \sys binary.

@@

\textbf{\sys Memory Manager:} When the binary executes, \sys's runtime support affects its execution through {\em (virtualizing) memory manager} (described in Section~\ref{sec:memory_virtulaization}) and {\em (coalescing) task scheduler} (described in Section~\ref{sec:task_coalescing}). The \sys binary executes its tasks correctly, with consistent memory state, due to \sys's virtual memory mechanism. Relying on programmer or compiler annotation of accesses to memory locations that might be shared between tasks, \sys's memory virtualization {\em pages} these data to SRAM from FRAM as they are needed. Tasks operate, accessing SRAM only, demand-paging data to accommodate a SRAM smaller than FRAM\todo{Sentence unclear}{Brandon}. When a task completes, \sys commits modified, paged data back to its original FRAM location atomically ensuring subsequent tasks page in correct memory state.

\textbf{\sys Task Scheduler:} \sys runs a lightweight task scheduler that uses {\em task coalescing} to make \sys's statically defined tasks efficiently use available energy. By default, tasks run in sequence and each task commits as it completes, potentially incurring unnecessary overhead for commits between consecutive, non-failing tasks. \sys dynamically coalesces consecutive tasks by deferring the commit of an earlier task until the completion of a later task. \sys's memory management mechanism facilitates coalescing because \sys can defer an earlier task's commit by simply buffering modified, paged data as the later task executes. After coalescing a sequence of tasks, \sys commits all tasks' updates to FRAM, together, combining tasks updates to the same pages and minimizing the commit overhead.

>>>>

\noindent \textbf{\sys Programming Model:} To use \sys, a programmer first writes plain, imperative C code. The programmer then has an option to {\em manually} or {\em automatically} translate the program into code for \sys's task-based programming model. To manually translate, the programmer decomposes the program into tasks, and annotates memory accesses that manipulate data shared by multiple tasks. To automatically translate, the programmer simply uses \sys's compiler (described in Section~\ref{sec:compiler}), which decomposes a program into tasks and annotates accesses to task-shared data. After translating to task-based code and compiling, the programmer has an executable \sys binary.

@@

\noindent \textbf{\sys Memory Manager:} When the binary executes, \sys's runtime support affects its execution through {\em (virtualizing) memory manager} (described in Section~\ref{sec:memory_virtulaization}) and {\em (coalescing) task scheduler} (described in Section~\ref{sec:task_coalescing}). The \sys binary executes its tasks correctly, with consistent memory state, due to \sys's virtual memory mechanism. Relying on programmer or compiler annotation of accesses to memory locations that might be shared between tasks, \sys's memory virtualization {\em pages} these data to SRAM from FRAM as they are needed. Tasks operate, accessing SRAM only, demand-paging data to accommodate a SRAM smaller than FRAM\todo{Sentence unclear}{Brandon}. When a task completes, \sys commits modified, paged data back to its original FRAM location atomically ensuring subsequent tasks page in correct memory state.

\noindent \textbf{\sys Task Scheduler:} \sys runs a lightweight task scheduler that uses {\em task coalescing} to make \sys's statically defined tasks efficiently use available energy. By default, tasks run in sequence and each task commits as it completes, potentially incurring unnecessary overhead for commits between consecutive, non-failing tasks. \sys dynamically coalesces consecutive tasks by deferring the commit of an earlier task until the completion of a later task. \sys's memory management mechanism facilitates coalescing because \sys can defer an earlier task's commit by simply buffering modified, paged data as the later task executes. After coalescing a sequence of tasks, \sys commits all tasks' updates to FRAM, together, combining tasks updates to the same pages and minimizing the commit overhead.
